Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-18 chapters/introduction/introduction.tex
minor change
minor changes

Most recent geo-calibration algorithms are deterministic systems
\todo{citations}. 
Deterministic systems have some obvious drawbacks: 1) they cannot
model the inherent uncertainties from images of ambiguous scenes, and
2) without a proper modeling of the uncertainty, the subsequent
process can yield overly confident predictions. To address these
problems, we propose to build probabilistic systems for camera
geo-calibration.

@@

  \item \textbf{Constraint for Location and Orientation:}
  The previous algorithm only estimates locations approximately
  due to the limited capacity of the deep neural network. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of the constraint function, feed the aerial
  image of a given location and orientation to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency between the two
  and use it as the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

@@

\todo{describe problems to solve}

>>>>

Most recent geo-calibration algorithms are deterministic
systems~\cite{baatz2012large,doersch2012what,li2012worldwide}.
Deterministic systems have some obvious drawbacks: 1) they cannot
model the inherent uncertainties from images of ambiguous scenes, and
2) without a proper modeling of the uncertainty, the subsequent
process can yield overly confident predictions. To address these
problems, we propose to build probabilistic systems for camera
geo-calibration.

@@

  \item \textbf{Constraint for Location and Orientation:}
  The previous algorithm only estimates locations approximately
  due to the limited capacity of the deep neural network. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of the constraint function, we feed the aerial
  image of a given location and orientation to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency between the two
  and use it as the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

@@
